Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-17 paper/uist_2016/paper.tex
first draft of the table

@@

>>>>

%added for table
\usepackage{multirow}
\usepackage[table,xcdraw]{xcolor}
\usepackage{adjustbox}
\usepackage{amsmath}

@@

\begin{table*}[t]
	\centering
	\caption{My caption}
	\begin{adjustbox}{width=1\textwidth}
		\small
		\label{my-label}
		\begin{tabular}{ccccccccccccccccc}
			\cline{4-17}
			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{2}{c|}{GPS usage}                                                                                       & \multicolumn{2}{c|}{Traveller type}                                                                                  & \multicolumn{2}{c|}{Accompany}                                                                                               & \multicolumn{6}{c|}{Distance}                                                                                                                                                                                                                                                                                                            & \multicolumn{2}{c|}{Visit frequency}                                                                                 \\ \cline{4-17} 
			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{1}{c|}{GPS user}                             & \multicolumn{1}{c|}{non-GPS user}                        & \multicolumn{1}{c|}{Frequent}                             & \multicolumn{1}{c|}{Non-frequent}                        & \multicolumn{1}{c|}{Alone}                                     & \multicolumn{1}{c|}{Not alone}                              & \multicolumn{1}{c|}{0}                                & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{2}                               & \multicolumn{1}{c|}{3}                               & \multicolumn{1}{c|}{4}                               & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{Most}                                 & \multicolumn{1}{c|}{Least}                               \\ \hline
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}60}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}74}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}47}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81}          \\ \cline{3-17} 
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}66.67\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}42.02\%}     & \multicolumn{1}{c|}{50.83\%}                              & \multicolumn{1}{c|}{47.46\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}55.00\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.22\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}43.66\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}51.56\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}27.66\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.20\%}     \\ \cline{3-17} 
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{l|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$\\ p =0.0016\end{tabular}}  & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$\\ p = 0.3953\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 31.812$\\ p \textless0.0001\end{tabular}}  & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$\\ p = 0.0028\end{tabular}}                                                                                                                                                                                                                   & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$\\ p = 0.0001\end{tabular}} \\ \cline{2-17} 
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{58}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{57}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{64}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17} 
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{48.28\%}                              & \multicolumn{1}{c|}{56.30\%}                             & \multicolumn{1}{c|}{53.33\%}                              & \multicolumn{1}{c|}{54.39\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}61.70\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89.74\%}        & \multicolumn{1}{c|}{60.00\%}                          & \multicolumn{1}{c|}{25.00\%}                         & \multicolumn{1}{c|}{55.56\%}                         & \multicolumn{1}{c|}{59.15\%}                         & \multicolumn{1}{c|}{50.00\%}                         & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{52.17\%}                              & \multicolumn{1}{c|}{56.25\%}                             \\ \cline{3-17} 
			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Memorability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$\\ p =0.1992\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$\\ p = 0.4478\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,  133) = 9.016$\\ p = 0.0013\end{tabular}}        & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$\\ p = 0.4467\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$\\ p =  0.3987\end{tabular}}                        \\ \hline
			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{19}                                   & \multicolumn{1}{c|}{67}                                  & \multicolumn{1}{c|}{61}                                   & \multicolumn{1}{c|}{25}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{13}                              & \multicolumn{1}{c|}{30}                              & \multicolumn{1}{c|}{32}                              & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}34}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}27}          \\ \cline{3-17} 
			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{68.42\%}                              & \multicolumn{1}{c|}{80.60\%}                             & \multicolumn{1}{c|}{77.05\%}                              & \multicolumn{1}{c|}{80.00\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81.69\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.00\%}        & \multicolumn{1}{c|}{80.00\%}                          & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{69.23\%}                         & \multicolumn{1}{c|}{90.00\%}                         & \multicolumn{1}{c|}{75.00\%}                         & \multicolumn{1}{c|}{0.00\%}                          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}70.59\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}88.89\%}     \\ \cline{3-17} 
			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$\\ p = 0.2073\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$\\ p = 0.4947\end{tabular}}                          & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 20.956$\\ p \textless 0.0001\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$\\ p= 0.1709\end{tabular}}                                                                                                                                                                                                                                               & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$\\ p =0.078\end{tabular}}    \\ \cline{2-17} 
			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}91}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}37}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}53}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}49}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}6}       & \multicolumn{1}{c|}{33}                                   & \multicolumn{1}{c|}{58}                                  \\ \cline{3-17} 
			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}69.23\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}84.27\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}85.71\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.86\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.09\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}71.79\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.91\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}79.59\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}33.33\%} & \multicolumn{1}{c|}{69.70\%}                              & \multicolumn{1}{c|}{81.03\%}                             \\ \cline{3-17} 
			\multicolumn{1}{|l|}{\multirow{-6}{*}{\rotatebox{90}{Believability}}} & \multicolumn{1}{l|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$\\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$\\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$\\ p =0.086\end{tabular}}           & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$\\ p = 0.0726\end{tabular}}                                                                                                                                                                                                                    & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$\\ p = 0.1647\end{tabular}}                          \\ \hline
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{60}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{74}                                        & \multicolumn{1}{c|}{20}                                     & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{67}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{47}                                   & \multicolumn{1}{c|}{81}                                  \\ \cline{3-17} 
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{13.33\%}                              & \multicolumn{1}{c|}{9.24\%}                              & \multicolumn{1}{c|}{12.50\%}                              & \multicolumn{1}{c|}{6.78\%}                              & \multicolumn{1}{c|}{12.16\%}                                   & \multicolumn{1}{c|}{10.00\%}                                & \multicolumn{1}{c|}{20.00\%}                          & \multicolumn{1}{c|}{37.50\%}                         & \multicolumn{1}{c|}{5.56\%}                          & \multicolumn{1}{c|}{7.04\%}                          & \multicolumn{1}{c|}{13.43\%}                         & \multicolumn{1}{c|}{10.00\%}                         & \multicolumn{1}{c|}{14.89\%}                              & \multicolumn{1}{c|}{9.88\%}                              \\ \cline{3-17} 
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$\\ p = 0.2804\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$\\ p = 0.3948\end{tabular}}                                  & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$\\ p = 0.1492\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$\\ p = 0.2858\end{tabular}}                           \\ \cline{2-17} 
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}58}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}120}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}66}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10}      & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17} 
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.86\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}9.24\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20.83\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}1.75\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12.77\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}25.64\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}   & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}11.11\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}19.70\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}40.00\%} & \multicolumn{1}{c|}{10.87\%}                              & \multicolumn{1}{c|}{17.50\%}                             \\ \cline{3-17} 
			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Desirability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$\\ p = 0.0034\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$\\ p = 0.059\end{tabular}}          & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$\\ p= 0.0729\end{tabular}}                                                                                                                                                                                                                     & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$\\ p = 0.2288\end{tabular}}                         \\ \hline
		\end{tabular}
	\end{adjustbox}
\end{table*}
